Analyses

### 2023-01-30 analyses.RmD
- major updates to preprint

---
title: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache = T)
options(digits = 3, width = 250, scipen=999)
```

Here you can find the code and the results of all analyses. To see the code, click on button "Code". Alternatively, you can download the rmd file from the github repo.

@@

Load packages.

```{r r-setup, results='hide'}
# install packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")

# define packages
packages <- c("brms", "devtools", "GGally", "ggplot2", 
              "gridExtra", "kableExtra", "knitr", "lavaan", "lme4", 
              "magrittr", "mice", "mvnormalTest", 
              "PerFit", "psych", "quanteda.textstats", "semTools", "tidyverse")

# load packages
lapply(c(packages, "td"), library, character.only = TRUE)
```

## Custom functions

Find variables in dataset.

```{r}
find_var <- function(name, data = doc)(
  # finds the variables names for an item for each wave
    data %>% 
    filter(Label == name) %>% 
    select(variable) %>% 
    unlist() %>% 
    set_names(sub("\\_.*", "", .))
)
```

Extract characteristics from fitted lmer models.

```{r}
get_specs <- function(model){
    # Get mean, max, and min values

    dat <- coefficients(model)$wave
    specs <- data.frame(
    sd = attr(VarCorr(model), "sc"),
    min = min(dat),
    max = max(dat),
    mean = mean(dat$`(Intercept)`)
  )
}
```

Get data from fitted lmer objects for descriptives.

```{r}
get_dat <- function(model){
  coefficients(model)$wave %>% 
  tibble::rownames_to_column("wave") %>% 
  rename(value = "(Intercept)") %>% 
  mutate(wave = as.integer(.$wave),
         value = as.numeric(.$value)) 
} 
```

Determine average reliability for measures across waves

```{r}
get_rel <- function(data, waves=24){

  # extract average reliability from lavaan fitted cfa with several groups
  reliability(data) %>% 
  unlist() %>% 
  matrix(5, waves) %>% 
  as.data.frame() %>% 
  set_rownames(c("alpha", "omega", "omega2", "omega3", "avevar")) %>% 
  summarise(omega = rowMeans(.["omega",])) %>% 
  return()
}
```

Make graph of variables' development.

```{r}
make_graph <- function(model, title, ll, ul, line = FALSE, labels = FALSE, lmer=TRUE, legend=TRUE){

    if(isTRUE(lmer)){
      dat <- get_dat(model)
    } else{
    dat <- model
  }

  graph <- 
    ggplot(dat, aes(wave, value, color = dimension)) +
    {if(legend) theme(
      legend.position = c(0.85, 0.8),
      legend.title = element_blank()
      )} + 
    {if(!legend) theme(
      legend.position = "none"
    )} +
    theme(axis.title.x=element_blank()) +
    coord_cartesian(ylim = c(ll, ul)) +
    ggtitle(title) +
    {if(line) geom_smooth(se = FALSE, method = 'loess')} +
    # geom_point() +
    scale_color_manual(values=c("dodgerblue3", "deepskyblue2", "magenta2", "green2", "red"))
  graph
}
```

Get data of lmer objects for results.

```{r}
# get data
get_dat_res <- function(data_aff_neg, data_aff_pos, data_life_sat, type){

  dat_fig_results <- 
  broom.mixed::tidy(data_aff_neg, conf.int = T) %>% 
  mutate(dv = "aff_neg") %>% 
  rbind(
    broom.mixed::tidy(data_aff_pos, conf.int = T) %>% 
    mutate(dv = "aff_pos")
  ) %>% 
  rbind(
    broom.mixed::tidy(data_life_sat, conf.int = T) %>% 
    mutate(dv = "life_sat")
  ) %>% 
  mutate(
    type = ifelse(grepl(".*_w\\>", .$term), "within", "between"),
    iv = gsub("_(w|b)\\>", "", .$term)
         ) %>%
  mutate(
    type = factor(.$type, 
                  levels = c("within", "between")),
    dv = factor(.$dv, 
                levels = c("life_sat", "aff_pos", "aff_neg"),
                labels = c("Life satisfaction", "Positive affect", "Negative affect"))
  ) %>% 
  select(dv, iv, type, estimate, conf.low, conf.high, p.value)

  # select Social Media type of activity
  if(type == "activity") {
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_read", "soc_med_like_share", "soc_med_post")) %>% 
    mutate(
      iv = factor(.$iv, 
                  levels = c("soc_med_post", "soc_med_like_share", "soc_med_read"), 
                  labels = c("Posting", "Liking & Sharing", "Reading"))
    )
  } else if(type == "channel"){
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw")) %>% 
    mutate(iv = factor(.$iv, levels = c("soc_med_yt", "soc_med_wa", "soc_med_ig", "soc_med_tw", "soc_med_fb"), labels = c("YouTube", "WhatsApp", "Instagram", "Twitter", "Facebook")))
  } else if(type == "control"){
    dat_fig_results %<>%
      filter(iv %in% c("male", "health", "loc_cntrl_int_m", "employment_facPublic service", "act_spo", "sat_dem")) %>% 
      mutate(iv = factor(.$iv, levels = c("male", "health", "loc_cntrl_int_m", "employment_facPublic service", "act_spo", "sat_dem"), 
                         labels = c("Male", "Health", "Internal locus of control", "Employed public service", "Sport", "Satisfaction democracy")))
  }
  return(dat_fig_results)
}

```

Make graph of effects

```{r}
make_graph_res <- function(data_1, data_2 = NULL, sesoi = NULL){
  ggplot(data_1, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("grey40", "deepskyblue")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high),
                lwd = .75, height = .2) +
  geom_point(size = 2) +
  {if(!is.null(data_2)) geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), data_2,
                lwd = .75, height = .2, color = "grey",
                position = position_nudge(y = -.3)
                )} +
  {if(!is.null(data_2)) geom_point(data = data_2, size = 2, color = "grey",
             position = position_nudge(y = -.3)
             )} +
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data_1, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data_1, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data_1, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data_1, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed")} +
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=.1), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=-.1), colour="darkgrey", linetype = "dashed")} +   theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 0)
    ) +
  facet_grid(rows = vars(type),
             cols = vars(dv),
             scales = "free",
             space = "free_y") 
}
```

Extract factor scores.

```{r}
get_fs <- function(model) {
  # the aim is to get factor scores on original scaling
  # hence export factor values for all items
  # then compute average
  dat_ov <- lavaan::lavPredict(model, type = "ov", assemble = TRUE) %>% 
    mutate(fs = rowMeans(.[1:3]))
  return(dat_ov$fs)
}
```

# Data Wrangling

```{r}
doc <- read_csv("documentation/10094_vi_de_v4_0.csv")
d_raw <- read_csv("data/10094_da_de_v4_0.csv")
```

Identify the names of each item for each wave.

```{r}
# identify variable names of items, using custom function
health <- find_var("Gesundheitszustand") # wsn't collected at wave 21
aff_neg_1 <- find_var("Depressivitaet: einsam")
aff_neg_2 <- find_var("Depressivitaet: aergerlich")
aff_neg_3 <- find_var("Depressivitaet: so niedergeschlagen")
aff_neg_4 <- find_var("Depressivitaet: sehr nervoes")
aff_neg_5 <- find_var("Depressivitaet: aengstlich")
aff_neg_6 <- find_var("Depressivitaet: bedrueckt und traurig")
aff_pos_1 <- find_var("Depressivitaet: ruhig und gelassen")
aff_pos_2 <- find_var("Depressivitaet: gluecklich")
aff_pos_3 <- find_var("Depressivitaet: voller Energie")
act_wrk <- find_var("Zuhause verlassen: Arbeit")
act_spo <- find_var("Zuhause verlassen: Sport")
act_frn <- find_var("Zuhause verlassen: Freunde oder Verwandte treffen")
act_sho <- find_var("Zuhause verlassen: Essen einkaufen")
act_pet <- find_var("Zuhause verlassen: Haustier ausfuehren")
sat_dem <- find_var("Demokratiezufriedenheit: Oesterreich")
work_h <- find_var("Arbeitsstunden: Jetzt pro Woche")
work_homeoff <- find_var("Aenderung berufliche Situation: Home-Office")
hh_income <- find_var("Aktuelles Haushaltseinkommen")
med_txt_kro <- find_var("Mediennutzung: Kronen Zeitung oder www.krone.at")
med_txt_sta <- find_var("Mediennutzung: Der Standard oder derstandard.at")
med_txt_pre <- find_var("Mediennutzung: Die Presse oder diepresse.com")
med_txt_oes <- find_var("Mediennutzung: Oesterreich oder oe24.at")
med_txt_kur <- find_var("Mediennutzung: Kurier oder kurier.at")
med_txt_slz <- find_var("Mediennutzung: Salzburger Nachrichten oder salzburg.at")
med_txt_son <- find_var("Mediennutzung: Sonstige oesterreichische Tageszeitungen")
med_vid_orf <- find_var("Mediennutzung: ORF (Nachrichten)")
med_vid_pri <- find_var("Mediennutzung: Privatfernsehen (Nachrichten)")
soc_med_fb <- find_var("Soziale Medien: Facebook")
soc_med_tw <- find_var("Soziale Medien: Twitter")
soc_med_ig <- find_var("Soziale Medien: Instagram")
soc_med_yt <- find_var("Soziale Medien: Youtube")
soc_med_wa <- find_var("Soziale Medien: WhatsApp")
soc_med_read <- find_var("Soziale Medien Aktivitaet: Postings zu Corona anderer lesen")
soc_med_like_share <- find_var("Soziale Medien Aktivitaet: Postings liken, teilen oder retweeten")
soc_med_post <- find_var("Soziale Medien Aktivitaet: selber Postings zu Corona verfassen")
life_sat <- find_var("Lebenszufriedenheit")
risk_prop <- find_var("Risikobereitschaft")
loc_cntrl_int_1 <- find_var("Psychologie: habe Leben selbst in der Hand")
loc_cntrl_int_2 <- find_var("Psychologie: Belohnung durch Anstrengung")
loc_cntrl_int_3 <- find_var("Psychologie: Fremdbestimmung")
loc_cntrl_int_4 <- find_var("Psychologie: Schicksal")
```

Select variables.

```{r}
d_wide <- d_raw %>% 
  select(
    id = RESPID,
    gender = SD_GENDER,
    acc_bal = SD_ACCESS_BALCONY,
    acc_gar = SD_ACCESS_GARDEN,
    year_birth = SD_BIRTHYEAR,
    born_aus = SD_BORN_AUSTRIA,
    born_aus_prnts = SD_MIGR_BACKGR,
    county = SD_BULA,
    edu = SD_EDU,
    employment = SD_EMPLSTATUS_FEB2020,
    hh_adults = SD_HH_ADULTS,
    hh_child18 = SD_HH_CHILD18,
    hh_child17 = SD_HH_TEENS,
    hh_child14 = SD_HH_CHILD14,
    hh_child5 = SD_HH_CHILD5,
    hh_child2 = SD_HH_CHILD2,
    hh_oldfam = SD_HH_OLDERFAM,
    hh_outfam = SD_HH_OUTERFAM,
    hh_partner = SD_HH_PARTNER,
    # hh_income = SD_HHINCOME_FEB2020,
    home_sqm = SD_HOME_SQM,
    home_owner = SD_HOMEOWNER,
    # work_h = SD_WORKHOURS_FEB2020,
    health = all_of(health),
    life_sat = all_of(life_sat),
    aff_neg_1 = all_of(aff_neg_1),
    aff_neg_2 = all_of(aff_neg_2),
    aff_neg_3 = all_of(aff_neg_3),
    aff_neg_4 = all_of(aff_neg_4),
    aff_neg_5 = all_of(aff_neg_5),
    aff_neg_6 = all_of(aff_neg_6),
    aff_pos_1 = all_of(aff_pos_1),
    aff_pos_2 = all_of(aff_pos_2),
    aff_pos_3 = all_of(aff_pos_3),
    act_wrk = all_of(act_wrk),
    act_spo = all_of(act_spo),
    act_frn = all_of(act_frn),
    act_sho = all_of(act_sho),
    act_pet = all_of(act_pet),
    sat_dem = all_of(sat_dem),
    sat_dem = all_of(sat_dem),
    work_h = all_of(work_h),
    work_homeoff = all_of(work_homeoff),
    hh_income = all_of(hh_income),
    med_txt_kro = all_of(med_txt_kro),
    med_txt_sta = all_of(med_txt_sta),
    med_txt_pre = all_of(med_txt_pre),
    med_txt_oes = all_of(med_txt_oes),
    med_txt_kur = all_of(med_txt_kur),
    med_txt_slz = all_of(med_txt_slz),
    med_txt_son = all_of(med_txt_son),
    med_vid_orf = all_of(med_vid_orf),
    med_vid_pri = all_of(med_vid_pri),
    soc_med_fb = all_of(soc_med_fb),
    soc_med_tw = all_of(soc_med_tw),
    soc_med_ig = all_of(soc_med_ig),
    soc_med_yt = all_of(soc_med_yt),
    soc_med_wa = all_of(soc_med_wa),
    soc_med_like_share = all_of(soc_med_like_share),
    soc_med_read = all_of(soc_med_read),
    soc_med_post = all_of(soc_med_post),
    risk_prop = all_of(risk_prop),
    loc_cntrl_int_1 = all_of(loc_cntrl_int_1),
    loc_cntrl_int_2 = all_of(loc_cntrl_int_2),
    loc_cntrl_int_3 = all_of(loc_cntrl_int_3),
    loc_cntrl_int_4 = all_of(loc_cntrl_int_4)
  )
```

Make new documentation with selected variables.

```{r}
doc_selected <- filter(doc, variable %in% c(
  "RESPID",
  "SD_GENDER",
  "SD_ACCESS_BALCONY",
  "SD_ACCESS_GARDEN",
  "SD_BIRTHYEAR",
  "SD_BORN_AUSTRIA",
  "SD_MIGR_BACKGR",
  "SD_BULA",
  "SD_EDU",
  "SD_EMPLSTATUS_FEB2020",
  "SD_HH_ADULTS",
  "SD_HH_CHILD18",
  "SD_HH_TEENS",
  "SD_HH_CHILD14",
  "SD_HH_CHILD5",
  "SD_HH_CHILD2",
  "SD_HH_OLDERFAM",
  "SD_HH_OUTERFAM",
  "SD_HH_PARTNER",
  "SD_HHINCOME_FEB2020",
  "SD_HOME_SQM",
  "SD_HOMEOWNER",
  "SD_WORKHOURS_FEB2020",
  health[1],
  life_sat[1],
  aff_neg_1[1],
  aff_neg_2[1],
  aff_neg_3[1],
  aff_neg_4[1],
  aff_neg_5[1],
  aff_neg_6[1],
  aff_pos_1[1],
  aff_pos_2[1],
  aff_pos_3[1],
  act_wrk[1],
  act_spo[1],
  act_frn[1],
  act_sho[1],
  act_pet[1],
  sat_dem[1],
  work_h[1],
  work_homeoff[1],
  hh_income[1],
  med_txt_kro[1],
  med_txt_sta[1],
  med_txt_pre[1],
  med_txt_oes[1],
  med_txt_kur[1],
  med_txt_slz[1],
  med_txt_son[1],
  med_vid_orf[1],
  med_vid_pri[1],
  soc_med_fb[1],
  soc_med_tw[1],
  soc_med_ig[1],
  soc_med_yt[1],
  soc_med_wa[1],
  soc_med_like_share[1],
  soc_med_post[1],
  soc_med_read[1],
  risk_prop[1],
  loc_cntrl_int_1[1],
  loc_cntrl_int_2[1],
  loc_cntrl_int_3[1],
  loc_cntrl_int_4[1]
  ))
```

Recode Variables

```{r}
d_wide %<>%
  mutate_at(vars(everything(.)), funs(na_if(., 88))) %>%
  mutate_at(vars(everything(.)), funs(na_if(., 99))) %>%
  mutate(
    male = 2 - .$gender,
    age = 2021 - .$year_birth,
    res_vienna = recode(.$county, `8` = 1L, .default = 0L,),
    born_aus = 2 - .$born_aus,
    home_owner = 2 - .$home_owner,
    employment_fac = factor(.$employment, 
                           labels = c("Unemployed",
                                      "Industrie",
                                      "Public service",
                                      "Self-employed",
                                      "Retired",
                                      "Housekeeping",
                                      "Student",
                                      "Incapacitated",
                                      "Parental Leave"),
                            levels = c(4, 1:3, 5:8, 10) # make unemployment reference cat
                           ),
    edu_fac = factor(.$edu,
                     labels = c("No degree", 
                                "Middle school",
                                "Vocational school",
                                "Technical school",
                                "High school",
                                "Applied high school",
                                "State college",
                                "Bachelor",
                                "Master",
                                "PhD")
                     ))
```

Make data from wide to long.

```{r}
d_long <-
  d_wide %>% 
  pivot_longer(
    cols = health...W1:loc_cntrl_int_4...W9,
    names_to = "item",
    values_to = "value"
  ) %>% 
  separate(item, c("item", "wave"), sep = "\\.\\.\\.", extra = "merge") %>% 
  pivot_wider(names_from = "item", values_from = "value")
```

Recode values.

```{r}
# recode such that higher values imply more strength / align with wording
d_long %<>% 
  mutate_at(vars(med_txt_kro:med_vid_pri, health, sat_dem, soc_med_fb:soc_med_post), 
            funs(recode(., `1` = 5L, `2` = 4L, `3` = 3L, `4` = 2L, `5` = 1L))) %>% 
  mutate_at(vars(loc_cntrl_int_1:loc_cntrl_int_4), 
            funs(recode(., `1` = 4L, `2` = 3L, `3` = 2L, `4` = 1L))) %>% 
  mutate_at(vars(born_aus_prnts), 
            funs(recode(., `3` = 0L, `2` = 2L, `1` = 1L)))

# recode inverted items
d_long %<>%
  mutate_at(vars(loc_cntrl_int_3, loc_cntrl_int_4), 
            funs(recode(., `1` = 4L, `2` = 3L, `3` = 2L, `4` = 1L)))

# recode other
d_long %<>%
  mutate(
    wave = gsub("W", "", .$wave) %>% as.integer(),
    id = as.integer(id)
  )
```

Order dataset. First id, then wave.

```{r}
d_long %<>%
  arrange(id, wave)
```

# Impute data

Determine amount of missingness per respondent per wave. Because calculation takes long, this chunk is not executed but loaded from memory. To execute, set eval == TRUE.

```{r eval=TRUE}
vars_used <- c("life_sat", "aff_pos_1", "aff_pos_2", "aff_pos_3", "aff_neg_1", "aff_neg_2", "aff_neg_3", "aff_neg_4", "aff_neg_5", "aff_neg_6", "soc_med_read", "soc_med_like_share", "soc_med_post", "soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw", "age", "male", "born_aus", "born_aus_prnts", "edu_fac", "employment_fac", "health", "res_vienna", "acc_bal", "acc_gar", "home_sqm", "med_txt_kro", "med_txt_sta", "med_txt_pre", "med_txt_oes", "med_txt_kur", "med_txt_slz", "med_txt_son", "med_vid_orf", "med_vid_pri", "risk_prop", "loc_cntrl_int_1", "loc_cntrl_int_2", "loc_cntrl_int_3", "loc_cntrl_int_4", "act_wrk", "act_spo", "act_frn", "act_sho", "act_pet", "sat_dem")

# filter respondents with more than 50% missing data
d_long_filt <- 
  d_long %>% 
  mutate(na_perc = rowSums(is.na(select(., all_of(vars_used))) / ncol(select(., all_of(vars_used))))) %>% 
  filter(na_perc < .5)

# impute missing data
# exclude social media use data, because they were measured only on selected waves and would lead to the imputation of too much missing data
vars_excl <- c("na_perc", "soc_med_read", "soc_med_like_share", "soc_med_post", "soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw")
incl_ma <- d_long_filt %>% 
  mutate(across(.cols = everything(), .fns = is.na))
incl_ma[vars_excl] <- FALSE

# init <- mice(select(d_long_test_filt, maxit = 0))
# pred_ma <- init$predictorMatrix
# pred_ma[, vars_excl] <- 0
d_long_imp <- mice(d_long_filt, method = "pmm", m = 1, maxit = 30, 
              where = incl_ma,
              # predictorMatrix = pred_ma, 
              seed = 180719, print = FALSE)
d_long_imp <- mice::complete(d_long_imp)

write_csv(d_long_imp, "data/data_imputed.csv")
```

Load imputed data from disc.

```{r}
d_long_imp <- read_csv("data/data_imputed.csv")
```

# Create within-between data

Create means for scales

```{r}
d_long_imp %<>%
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))
```

Create mean values for each person (between), and unique changes per wave (within).

```{r}
d_long_imp %<>% 
  group_by(id) %>% 
  mutate_at(vars(health:loc_cntrl_int_4, loc_cntrl_int_m), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()
```

And because later we want to rerun the results without imputed data, now the same for data without imputation.

```{r}
d_long %<>%
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))

d_long %<>% 
  group_by(id) %>% 
  mutate_at(vars(health:loc_cntrl_int_4, loc_cntrl_int_m), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()
```

# Measures
## Well-being
### Life satisfaction

```{r}
model_life_sat <- lmer(life_sat ~ (1 | id) + (1 | wave), d_long_imp)
summary(model_life_sat)
```

@@

Positive affect was measured as a scale. We hence first inspect factorial validity using CFA.

We first test assumption of multivariate normality.

```{r eval=FALSE}
mardia(d_long_imp %>% select(aff_pos_1, aff_pos_2, aff_pos_3))
```

Assumption of multivariate normal distributino was violated; hence, robust estimator will be used.

```{r}
model <- "
aff_pos =~ a1*aff_pos_1 + a2*aff_pos_2 + a3*aff_pos_3
"
cfa_aff_pos <- cfa(model, d_long_imp, group = "wave", estimator = "MLM")
summary(cfa_aff_pos, standardized = TRUE, fit = TRUE, estimates = FALSE)
```

The data fit the model very well, `r td::fit_txt(cfa_aff_pos)`.
Let's next inspect reliability

```{r}
rel_aff_pos <- get_rel(cfa_aff_pos)
rel_aff_pos
```

The average reliability across all waves was omega = `r rel_aff_pos`, hence good.

@@

```{r}
model_aff_pos <- lmer(aff_pos_m ~ (1 | id) + (1 | wave), d_long_imp)
summary(model_aff_pos)
```

Let's now export factor scores.

```{r}
d_long_imp$aff_pos_fs <- get_fs(cfa_aff_pos)
```

@@

Negative affect was measured as a scale. We hence inspect factorial validty using CFA.

We first test assumption of multivariate normality. (Warning, as these analyses take long and might require additional working memory, they're deactived currently.)

```{r eval=FALSE}
mardia(d_long_imp %>% select(aff_neg_1, aff_neg_2, aff_neg_3, aff_neg_4, aff_neg_5, aff_neg_6))
```

Assumption of multivariate normal distributino was violated; hence, robust estimator will be used.

```{r}
model <- "
aff_neg =~ a1*aff_neg_1 + a2*aff_neg_2 + a3*aff_neg_3 + a4*aff_neg_4 + a5*aff_neg_5 + a6*aff_neg_6
"
cfa_aff_neg <- cfa(model, d_long_imp, group = "wave", estimator = "MLM")
summary(cfa_aff_neg, standardized = TRUE, fit = TRUE, estimates = FALSE)
```

@@

```{r}
rel_aff_neg <- get_rel(cfa_aff_neg)
rel_aff_neg
```

The average reliability across all waves was omega = `r rel_aff_neg`, hence good.

```{r}
model_aff_neg <- lmer(aff_neg_m ~ (1 | id) + (1 | wave), d_long_imp)
summary(model_aff_neg)
```

Let's now export factor scores.

```{r}
d_long_imp$aff_neg_fs <- get_fs(cfa_aff_neg)
```

## Social media use
### Reading

```{r}
model_soc_med_read <- lmer(soc_med_read ~ (1 | id) + (1 | wave), d_long_imp)
summary(model_soc_med_read)
```

@@

```{r}
model_soc_med_like_share <- lmer(soc_med_like_share ~ (1 | id) + (1 | wave), d_long_imp)
summary(model_soc_med_like_share)
```

@@

```{r}
model_soc_med_post <- lmer(soc_med_post ~ (1 | id) + (1 | wave), d_long_imp)
summary(model_soc_med_post)
```

@@

```{r}
model_soc_med_fb <- lmer(soc_med_fb ~ (1 | id) + (1 | wave), d_long_imp)
summary(model_soc_med_fb)
```

@@

```{r}
model_soc_med_tw <- lmer(soc_med_tw ~ (1 | id) + (1 | wave), d_long_imp)
summary(model_soc_med_tw)
```

@@

```{r}
soc_med_tw_m <- d_long_imp %>% group_by(wave) %>% summarise(value = mean(soc_med_tw, na.rm = T))
soc_med_tw_m
```

@@

The only other variable that was measured as a scale was Locus of Control. Below I hence report the scale's factorial validity.

>>>>

---
title: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache=T, rows.print=20)
options(digits=2, width=260, scipen=999)
```

 - Here you can find the code and the results of all main analyses. 
 - To see the code, click on button "Code".
 - Alternatively, you can download the rmd file from the github repo.

@@

Load packages & workspace.

```{r r-setup, results='hide', cache=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")

# define packages
packages <- c("broom.mixed", "brms", "corrr", "devtools", "GGally", "ggplot2", 
              "gridExtra", "kableExtra", "knitr", "lavaan", "lme4", 
              "magrittr", "mice", "PerFit", "performance", "psych", 
              "quanteda.textstats", "scales", "semTools", "tidyverse")

# load packages
lapply(c(packages, "td"), library, character.only = TRUE)

# load workspace
load("data/workspace_1.RData")
```

# Measures

Let's first inspect the individual measures, how they develop over time. For positive and negative affect, we also look at their factor structure, as they're measured with multiple items.

## Well-being
### Life satisfaction

Let's inspect the development of life satisfaction across the study. We nest reponses inside participants and waves to get better results.

```{r}
fit_life_sat <- lmer(life_sat ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(fit_life_sat)
dat_fig_life_sat <- data.frame(type = "Life satisfaction", dimension = "Life satisfaction", 
                               get_dat(fit_life_sat))
make_graph(dat_fig_life_sat, "Life Satisfaction", 1, 10)
```

@@

@@

```{r}
model_aff_pos <- lmer(aff_pos_m ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_aff_pos)
dat_fig_aff_pos <- data.frame(type = "Affect", dimension = "Positive", 
                              get_dat(model_aff_pos))
make_graph(dat_fig_aff_pos, "Positive Affect", 1, 5)
```

Positive affect was measured as a scale. We hence also inspect factorial validity using CFA.

We first test assumption of multivariate normality. We focus on wave 1 here.

```{r}
d_long_100_imp %>%
  filter(wave == 1) %>% 
  select(aff_pos_1, aff_pos_2, aff_pos_3) %>% 
  mardia()
```

Assumption of multivariate normal distribution was violated; hence, robust estimator will be used.

```{r}
model <- "
aff_pos =~ a1*aff_pos_1 + a2*aff_pos_2 + a3*aff_pos_3
"
cfa_aff_pos <- cfa(model, d_long_100_imp, group = "wave", estimator = "MLM")
summary(cfa_aff_pos, standardized = TRUE, fit = TRUE, estimates = FALSE)
```

The data fit the model very well, `r td::fit_txt(cfa_aff_pos)`.
Let's next inspect reliability.

```{r}
rel_aff_pos <- get_rel(cfa_aff_pos)
```

The average reliability across all waves was omega = `r rel_aff_pos[[1]]`, hence good.

Let's now export factor scores for results reported in additional analyses.

```{r}
# with imputed data
cfa_aff_pos_50 <- cfa(model, d_long_50_imp, group = "wave", estimator = "MLM")
d_long_50_imp$aff_pos_fs <- get_fs(cfa_aff_pos_50)

# without imputed data
cfa_aff_pos <- cfa(model, d_long_50, group = "wave", estimator = "MLM")
d_long_50$aff_pos_fs <- get_fs(cfa_aff_pos)
```

@@

```{r}
model_aff_neg <- lmer(aff_neg_m ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_aff_neg)
dat_fig_aff_neg <- data.frame(type = "Affect", dimension = "Negative", get_dat(model_aff_neg))
make_graph(dat_fig_aff_neg, "Negative Affect", 1, 5)
```

Negative affect was measured as a scale. We hence inspect factorial validity using CFA.

We first test assumption of multivariate normality. We'll focus on wave 1 here.

```{r eval=T}
d_long_100_imp %>%
  filter(wave == 1) %>% 
  select(aff_neg_1, aff_neg_2, aff_neg_3, aff_neg_4, aff_neg_5, aff_neg_6) %>% 
  mardia()
```

Assumption of multivariate normal distribution was violated; hence, robust estimator will be used.

```{r}
model <- "
aff_neg =~ a1*aff_neg_1 + a2*aff_neg_2 + a3*aff_neg_3 + a4*aff_neg_4 + a5*aff_neg_5 + a6*aff_neg_6
"
cfa_aff_neg <- cfa(model, d_long_100_imp, group = "wave", estimator = "MLM")
summary(cfa_aff_neg, standardized = TRUE, fit = TRUE, estimates = FALSE)
```

@@

```{r}
rel_aff_neg <- get_rel(cfa_aff_neg)
```

The average reliability across all waves was omega = `r rel_aff_neg[[1]]`, hence good.

```{r}
model_aff_neg <- lmer(aff_neg_m ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_aff_neg)
```

Let's now export factor scores, necessary for results reported in additional analyses.

```{r}
# with imputed data
cfa_aff_neg_50 <- cfa(model, d_long_50_imp, group = "wave", estimator = "MLM")
d_long_50_imp$aff_neg_fs <- get_fs(cfa_aff_neg_50)

# without imputed data
cfa_aff_neg <- cfa(model, d_long_50, group = "wave", estimator = "MLM")
d_long_50$aff_neg_fs <- get_fs(cfa_aff_neg)
```

## Social media use

Social media use (and channels) were measured at waves 1, 2, 8, 17, 23, 28, and for everyone who was newly recruited during the study at the first wave.

### Reading

```{r}
model_soc_med_read <- lmer(soc_med_read ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_read)
dat_fig_soc_med_read <- data.frame(type = "Social media use", dimension = "Reading", 
                                   get_dat(model_soc_med_read))
make_graph(dat_fig_soc_med_read, "Social Media Reading", 1, 5)
```

@@

```{r}
model_soc_med_like_share <- lmer(soc_med_like_share ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_like_share)
dat_fig_soc_med_like_share <- data.frame(type = "Social media use", dimension = "Liking & Sharing",
                                         get_dat(model_soc_med_like_share))
make_graph(dat_fig_soc_med_like_share, "Social Media Liking and Sharing", 1, 5)
```

@@

```{r}
model_soc_med_post <- lmer(soc_med_post ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_post)
dat_fig_soc_med_post <- data.frame(type = "Social media use", dimension = "Posting", 
                                   get_dat(model_soc_med_post))
make_graph(dat_fig_soc_med_post, "Social Media Posting", 1, 5)
```

@@

```{r}
model_soc_med_fb <- lmer(soc_med_fb ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_fb)
dat_fig_soc_med_fb <- data.frame(type = "Social media channel", dimension = "Facebook", 
                                 get_dat(model_soc_med_fb))
make_graph(dat_fig_soc_med_fb, "Social Media Facebook", 1, 5)
```

@@

```{r}
model_soc_med_tw <- lmer(soc_med_tw ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_tw)
dat_fig_soc_med_tw <- data.frame(type = "Social media channel", dimension = "Twitter", 
                                 get_dat(model_soc_med_tw))
make_graph(dat_fig_soc_med_tw, "Social Media Twitter", 1, 5)
```

@@

```{r}
soc_med_tw_m <- 
  d_long_100_imp %>% 
  group_by(wave) %>% 
  summarise(value = mean(soc_med_tw, na.rm = T))
soc_med_tw_m
```

@@

The only other variable that was measured as a scale was Locus of Control. Below I hence report the scale's factorial validity. Waves for which not a sufficient number of respondents took part were excluded.
